The pollination trade-off

### 2018-08-22 paper/supp-info.Rmd
AIC fixed models tables
Issue #5

contingency_table[1:nrow(summ)] <- summ$delta_AIC

xtable::xtableFtable(contingency_table, method = "col.compact", 
             caption = paste('Comparison of the different random structures we considered. The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data. The 5th and 95th percentile are shown inside square brackets. Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."), 
         label = 'tab:table-aic-random-models')
```

>>>>

contingency_table[1:nrow(summ)] <- summ$delta_AIC
```{r table-aic-fixed-models, results= 'asis'}
drake::loadd(model_formula_ranking)

xtable::xtableFtable(contingency_table, method = "col.compact", 
             caption = paste('Comparison of the different random structures we considered. The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data. The 5th and 95th percentile are shown inside square brackets. Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."), 
         label = 'tab:table-aic-random-models')
model_formula_ranking$by_model_set %>% 
  dplyr::filter(scale == "community") %>%
  dplyr::mutate(delta_AIC = paste0(round(delta_AIC, 1), 
                                  " [", 
                                  round(delta_AIC_quantile_05, 1),
                                  " ,", 
                                  round(delta_AIC_quantile_95, 1),
                                  "]")) %>% 
  dplyr::group_by() %>%
  humanize(formula_long = TRUE) %>% 
  dplyr::mutate(fixed_formula = paste("~", fixed_formula)) %>%
  dplyr::arrange(pollen_category, delta_AIC_rank) %>%
  dplyr::select(pollen_category, fixed_formula, delta_AIC) %>%
  dplyr::rename(`pollen type` = pollen_category, 
                `fixed structure` = fixed_formula) %>%
  knitr::kable(caption = paste('Comparison of the different fixed structures we considered. The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data. The 5th and 95th percentile are shown inside square brackets."),
               booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::column_spec(column = 1, bold=T) %>%
  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
```
